The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-09-02 sections/abstract.tex
Rework abstract

\begin{abstract}
\julien[noline]{The abstract is preliminary.}
We present an ensemble of numerical simulations of the former Cordilleran ice sheet forced by present-day climatologies from five different datasets. Surface air temperature and precipitation rates from the NCEP/NCAR reanalysis, the Climate Forecast System Reanalysis, the ERA-Interim reanalysis and the North American Regional Reanalysis are used to force the ice sheet model PISM. Glacial conditions are mimicked by applying constant temperature offsets over the entire modelling domain, and a positive degree-day model is used to compute surface mass balance. The modelled ice sheet appears highly sensitive to the choice of climate forcing. Best results were obtained from the North American Regional Reanalysis, a high-resolution regional reanalysis which assimilates precipitation.
\end{abstract}

>>>>

\begin{abstract}
We present an ensemble of numerical simulations of the Cordilleran Ice Sheet during the Last Glacial Maximum performed with the Parallel Ice Sheet Model, using temperature offsets from present-day climatologies from five different datasets. Monthly mean surface air temperature and monthly precipitation from the NCEP/NCAR reanalysis, the Climate Forecast System Reanalysis, the ERA-Interim reanalysis and the North American Regional Reanalysis are used to compute surface mass balance using a positive degree-day model. Modelled ice sheet outlines and volumes appear highly sensitive to the choice of climate forcing. Best results were obtained using the North American Regional Reanalysis, a high-resolution regional climate reanalysis.
\end{abstract}
